Optimal Fitting of Planar Curves to Prescribed Constraints

### 2014-02-02 idp/documents/documentation/paper.tex
more subfloats

			\begin{figure}[htb]
				\centering
				\includegraphics[width=\textwidth]{content/output/examples_prototype.pdf}
				\caption{Prototype Curve Design Tool Examples (left: Fluttershy \cite{fluttershy})}
				\label{figure:examples_prototype}
			\end{figure}

			Figure \ref{figure:examples_prototype} shows some examples of curves designed using the prototype curve design tool. Point specification items are displayed as red dots, direction specification items are displayed green tangent lines and curvature specification items are displayed using blue circular arcs taken from the osculating circle.

			Example 1 shows how adjusting the arc length of an otherwise unconstrained curve allows the convenient creation of curcular arcs between two points.

@@

			Finally, example 5 demonstrates the ability of the MVC fairness to construct aesthetically pleasing, smooth curves. The indicators for the specification items were left out in this example to make it easier to judge the curve's smoothness.

>>>>

			\begin{figure}[htb]
				\centering
				\begin{subfigure}[b]{8 \textwidth / 13}
					\includegraphics[width=\textwidth]{content/output/examples_prototype_fluttershy.pdf}
					\caption{Fluttershy \cite{fluttershy}}
					\label{figure:examples_prototype_fluttershy}
				\end{subfigure}%
				\begin{subfigure}[b]{5 \textwidth / 13}
					\includegraphics[width=\textwidth]{content/output/examples_prototype_fairness.pdf}
					\caption{Fairness Measure Example}
					\label{figure:examples_prototype_fairness}
				\end{subfigure}
				\caption{Examples of curves designed using the prototype curve design tool. Point specification items are displayed as red dots, direction specification items are displayed green tangent lines and curvature specification items are displayed using blue circular arcs taken from the osculating circle.}
				\label{figure:examples_prototype}
			\end{figure}

			Figure \ref{figure:examples_prototype_fluttershy} shows a few curves designed using the prototype curve design tool. Example 1 demonstrates how adjusting the arc length of an otherwise unconstrained curve allows the convenient creation of curcular arcs between two points.

@@

			Finally, figure \ref{figure:examples_prototype_fairness} demonstrates the ability of the MVC fairness to construct aesthetically pleasing, smooth curves. The indicators for the specification items were left out in this example to make it easier to judge the curve's smoothness.
